DOM bridges and barriers: systematic review and survey

### 2025-12-11 reports/draft_results.qmd
update ms figures

freq_job_survey$bridge_barr <- factor(freq_job_survey$bridge_barr, levels = c("Bridge", "Barrier"))

@@

#stacked bar plots
freq_job_survey2$code_cat <- factor(freq_job_survey2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge", "Data barrier", "Ecological barrier", "Social barrier", "Implementation barrier"))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 11, 22), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 14, 28), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
#ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))

@@

#format data
freq_job_lit <- code_vars %>% 
  select(c(1, 27:29, 33:60)) %>%
  janitor::clean_names() %>%
  pivot_longer(2:4, names_to = "test", values_to = "fish_ship") %>%
  select(-c(test)) %>%
  pivot_longer(2:29, names_to = "sub_theme", values_to = "total") %>%
  group_by(fish_ship, sub_theme) %>%
  summarise(total = sum(total), 
            .groups = "drop") %>%
  filter(fish_ship == "Bycatch" | fish_ship == "Ship strikes" | fish_ship == "Overfishing" | fish_ship == "Entanglement" | fish_ship == "Avoid fisheries discharge")

@@

freq_job_lit$bridge_barr <- factor(freq_job_lit$bridge_barr, levels = c("Bridge", "Barrier"))

@@

#stacked bar plots
ggplot(freq_job_lit2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification = "left", 
          legend.text = element_text(size = 14, color = "black")) +
    xlab("") + 
    ylab("Proportion of theme (%)")

@@

#radar plots
freq_job_lit3 <- freq_job_lit %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>% 
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  # mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  # distinct(id, .keep_all = TRUE) %>%
  # select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 20, 40), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 15, 35), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))

@@

freq_pos_survey$bridge_barr <- factor(freq_pos_survey$bridge_barr, levels = c("Bridge", "Barrier"))

@@

#stacked bar plots
ggplot(freq_pos_survey2, aes(fill=code_level, y=value, x=position)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification.top = "left", 
          legend.title = element_text(size = 16, color = "black"), 
          legend.text = element_text(size = 14, color = "black"))+
    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
    xlab("") + 
    ylab("Proportion of theme (%)")+
    theme(axis.text.x = element_text(size = 14, color = "black", angle = 60, hjust = 1))

#ggsave("figures/ms_figs/position/stack_survey.png", width = 10, height = 8, units = c("in"))

>>>>

freq_job_survey$bridge_barr <- factor(freq_job_survey$bridge_barr, levels = c("Barrier", "Bridge"))

@@

#stacked bar plots
freq_job_survey2$code_cat <- factor(freq_job_survey2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge", "Data barrier", "Ecological barrier", "Social barrier", "Implementation barrier"))
#freq_job_survey2$bridge_barr <- factor(freq_job_survey2$bridge_barr, levels = c())

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 11, 22), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#A4BFB8", "#3B5948"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 14, 28), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#A4BFB8", "#3B5948"),#007172
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
#ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))

@@

#format data
freq_job_lit <- code_vars %>% 
  select(c(1, 27:29, 33:60)) %>%
  janitor::clean_names() %>%
  pivot_longer(2:4, names_to = "test", values_to = "fish_ship") %>%
  select(-c(test)) %>%
  pivot_longer(2:29, names_to = "sub_theme", values_to = "total") %>%
  group_by(fish_ship, sub_theme) %>%
  summarise(total = sum(total), 
            .groups = "drop") %>%
  filter(fish_ship == "Bycatch" | fish_ship == "Ship strikes")

@@

freq_job_lit$bridge_barr <- factor(freq_job_lit$bridge_barr, levels = c("Barrier", "Bridge"))

@@

#stacked bar plots
freq_job_lit2$code_cat <- factor(freq_job_lit2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Data barrier", "Ecological barrier", "Social barrier"))

ggplot(freq_job_lit2, aes(fill=code_cat, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#6D8C9E","#516875", "#F1DA9F", "#FED240", "#DBA400")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification = "left", 
          legend.text = element_text(size = 14, color = "black")) +
    xlab("") + 
    ylab("Percent of theme (%)")

@@

#radar plots
freq_job_lit3 <- freq_job_lit %>%
  group_by(fish_ship, bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(fish_ship, bridge_barr, code_name) %>% 
  mutate(n_subtotal = sum(total)) %>%
  reframe(value = (n_subtotal/n_total)*100) %>%
  ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(value))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 8, 16), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#A4BFB8", "#3B5948"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 16, 38), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#A4BFB8", "#3B5948"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))

@@

#freq_pos_survey$bridge_barr <- factor(freq_pos_survey$bridge_barr, levels = c("Bridge", "Barrier"))

@@

#stacked bar plots
freq_pos_survey2$code_cat <- factor(freq_pos_survey2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge", "Data barrier", "Ecological barrier", "Social barrier", "Implementation barrier"))

ggplot(freq_pos_survey2, aes(fill=code_cat, y=value, x=position)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#6D8C9E","#516875","#28343B", "#F1DA9F", "#FED240", "#DBA400", "#614900")) +
    facet_wrap(~bridge_barr, ncol = 1) +
    labs(fill = "") +
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification.top = "left", 
          legend.title = element_text(size = 16, color = "black"), 
          legend.text = element_text(size = 14, color = "black"))+
    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
    xlab("") + 
    ylab("Percent of theme (%)")+
    theme(axis.text.x = element_text(size = 14, color = "black", angle = 60, hjust = 1))

ggsave("figures/ms_figs/supp/position/stack_survey.png", width = 8, height = 11, units = c("in"))
